### 2015-12-07 ch03-lrm/LPMSmooth_ML_EG_JS_JL.tex
Fix bibliography

The measurement of \glspl{FRF} of dynamic systems is an important topic in the measurement society.  
\gls{FRF} measurement techniques are discussed, for instance, in 
\citep{Schoukens1998ImprFRFmeas,Schoukens2006LPM,guillaume1996,broersen1995transferfunction,Pintelon2010LPM1,Antoni2007,Pintelon2012}, and applied to real practical devices and systems \citep{Lim2010,Robinson1990,Behjat2010}, among others. 
Besides, \glspl{FRF} have been shown to provide a quick insight into the dynamic properties of \gls{LTI} systems. 
This capability is very useful for model validation and/or selection \citep{Pintelon2012}.

This paper uses nonparametric models in conjunction with the \gls{LPM}~\citep{Pintelon2010LPM1} to estimate the complex-valued \gls{FRF} in a linear \gls{LS} fashion. 
The advantage of using the nonparametric models is basically the non-involvement of the user in choosing a model order, i.e. no user interaction. Among the current nonparametric methods, the LPM method is chosen due to its superiority over the classical nonparametric methods (windowing) in suppressing leakage errors \citep{bendatPiersol1993,Oppenheim1983}. Consequently, the LPM estimate of the FRF is not hampered by leakage errors \citep{Pintelon2010LPM1,schoukens2010nonparametric}. Note that a more general discussion on the LPM, applied to noisy, real-valued data is found in \citep{fanGijbels1996LPM} with a specific focus on parametric tuning.

@@

Based on \citep{schoukens2010nonparametric}, the nonparametric method developed in this work is formulated in an output-error (OE) framework. A single-input-single-output (SISO) LTI system is considered. %, based on  \citep{schoukens2010nonparametric}. 
The input signal is a known random noise signal and the output signal is corrupted by measurement noise. This is depicted in Fig. 1 as a linear dynamic discrete-time SISO system, whose full mathematical model is of the form:
\begin{equation}\label{lpmtd1}
y(t)=G_0(q)u_0(t)+H_0(q)e(t)=G_0(q)u_0(t)+v(t)
\end{equation}
where $G_0(q)$ represents the dynamics of the system to be estimated, $u_0(t)$ is the input signal, $v(t)= H_0(q)e(t)$ is the noise source at the output, $H_0(q)$ is the noise dynamics, $e(t)$ is white noise, and $q^{-m}$ is the backwards shift operator ($q^{-m}x(t)$ = $x(t-m)$  with $m$ a positive integer). %\JL{$G_0(q)$ represents the dynamics of the system to be estimated.}

@@

Details of the theory pertaining to this section may be found in \citep{schoukens2010nonparametric}, basic aspects of which are presented below.

@@

The following assumptions are consistent with \citep{schoukens2010nonparametric} for an OE setup (Fig. \ref{lpmtdrep}):
\begin{assumption}
The SISO system $G_0$ and  the transients leakage spectrum $T_G$ are both smooth functions of the frequency.
\end{assumption}

@@

\subsubsection{The Hanning Window and the \glsentrytext{LPM}}\label{se:LPMFRFest}%\label{se:FRFhanningLPM}
\paragraph{Windowing}
The effect of windowing may be  exemplified by use of the Hanning window, which is very popular.  In a nutshell, the Hanning window is effective in reducing  the leakage errors, but  with a trade off of increased interpolation errors. %This is because the term $G_0(\Omega_k)U_0(k)$ in equation \eqref{lpmtd1} is not smooth and $G_0(\Omega_k)$ varies with the frequency. 
Pertinent details of the Hanning window are discussed in \citep{Schoukens2006LPM,Antoni2007FRF,schoukens2010nonparametric,Wellstead198155} and \citep{harris1978}.

@@

\paragraph{Formulation of the Linear LS LPM}
The LPM is formulated as a nonparametric local-linear-least-squares (LS) estimate using the full data record of length $N$ as outlined below \citep{schoukens2010nonparametric}. 
\citet[Section 7.2.2]{Pintelon2012} gives the general formulation of the \gls{LPM} for \gls{MIMO} systems. 
The formulation in this paper is a summary for a \gls{SISO} system.

@@

The smooth characteristics of $G_0(\Omega_k)$ and $T(\Omega_k)$ allow for the use of the Taylor series representations at the frequency lines $k+r$ in a frequency domain window of width $2n+1$, with a remainder $\mathcal{O}\left(\frac{r}{N}\right)^{(R+1)}$ of the first order Taylor series expansion \citep{schoukens2010nonparametric}, \emph{viz}:
\TODO{ordos are incorrect: notation-wise}
\begin{align}\label{lpmGTaylorS}
G_0(\Omega_{k+r})&=G_0(\Omega_k)+\sum_{p=1}^{R}g_p(k)r^p+\mathcal{O}\left(\frac{r}{N}\right)^{(R+1)},
\\
\label{lpmTTaylorS}
T(\Omega_{k+r})&=T(\Omega_k)+\sum_{p=1}^{R}t_p(k)r^p+N^{-1/2}\mathcal{O}\left(\frac{r}{N}\right)^{(R+1)},
\\
\text{where}&\ r\in\mathbb{W}_n,\quad \mathbb{W}_n = \{-n,-n+1,\dots,n\}
\end{align}

@@

The formulation of equation \eqref{eq:LSsolutionLPM} must take into account the fact that  a full rank of $K_n$ requires $n \geq R + 1$. The choice $n = R + 1$ results in the highest variance on the estimate, but with the smallest interpolation error \citep{schoukens2010nonparametric}. %(per JL)!

@@

\TODO{fix reference Section II}
Smoothing of the estimated \gls{FRF} requires the correct estimate of the impulse response. Unfortunately, the \gls{LPM} presented in \secref{se:theoryLPMandWindowing} and in \citep{schoukens2010nonparametric} does not estimate the \gls{FRF}  at the frequency $\Omega_0$ (i.e. \gls{DC} value of the \gls{FRF}), hence the subscript $\setminus\mathrm{DC}$ in equation \eqref{eq:impRespiDFT}. Consequently, the mean value of the corresponding estimated impulse response given in equation \eqref{eq:impRespiDFT} is not correct. This anomaly is rectified by developing a simple estimator of the mean value, presented below.

>>>>

The measurement of \glspl{FRF} of dynamic systems is an important topic in the measurement society.  
\gls{FRF} measurement techniques are discussed, for instance, in 
\citep{Schoukens1998ImprFRFmeas,Schoukens2006LPM,guillaume1996,broersen1995transferfunction,Pintelon2010LPM1,Antoni2007FRF,Pintelon2012}, and applied to real practical devices and systems \citep{Lim2010,Robinson1990,Behjat2010}, among others. 
Besides, \glspl{FRF} have been shown to provide a quick insight into the dynamic properties of \gls{LTI} systems. 
This capability is very useful for model validation and/or selection \citep{Pintelon2012}.

This paper uses nonparametric models in conjunction with the \gls{LPM}~\citep{Pintelon2010LPM1} to estimate the complex-valued \gls{FRF} in a linear \gls{LS} fashion. 
The advantage of using the nonparametric models is basically the non-involvement of the user in choosing a model order, i.e. no user interaction. Among the current nonparametric methods, the LPM method is chosen due to its superiority over the classical nonparametric methods (windowing) in suppressing leakage errors \citep{Bendat1993,Oppenheim1983}. Consequently, the LPM estimate of the FRF is not hampered by leakage errors \citep{Pintelon2010LPM1,Schoukens2009LPM}. Note that a more general discussion on the LPM, applied to noisy, real-valued data is found in \citep{Fan1996} with a specific focus on parametric tuning.

@@

Based on \citep{Schoukens2009LPM}, the nonparametric method developed in this work is formulated in an output-error (OE) framework. A single-input-single-output (SISO) LTI system is considered. %, based on  \citep{Schoukens2009LPM}. 
The input signal is a known random noise signal and the output signal is corrupted by measurement noise. This is depicted in Fig. 1 as a linear dynamic discrete-time SISO system, whose full mathematical model is of the form:
\begin{equation}\label{lpmtd1}
y(t)=G_0(q)u_0(t)+H_0(q)e(t)=G_0(q)u_0(t)+v(t)
\end{equation}
where $G_0(q)$ represents the dynamics of the system to be estimated, $u_0(t)$ is the input signal, $v(t)= H_0(q)e(t)$ is the noise source at the output, $H_0(q)$ is the noise dynamics, $e(t)$ is white noise, and $q^{-m}$ is the backwards shift operator ($q^{-m}x(t)$ = $x(t-m)$  with $m$ a positive integer). %\JL{$G_0(q)$ represents the dynamics of the system to be estimated.}

@@

Details of the theory pertaining to this section may be found in \citep{Schoukens2009LPM}, basic aspects of which are presented below.

@@

The following assumptions are consistent with \citep{Schoukens2009LPM} for an OE setup (Fig. \ref{lpmtdrep}):
\begin{assumption}
The SISO system $G_0$ and  the transients leakage spectrum $T_G$ are both smooth functions of the frequency.
\end{assumption}

@@

\subsubsection{The Hanning Window and the \glsentrytext{LPM}}\label{se:LPMFRFest}%\label{se:FRFhanningLPM}
\paragraph{Windowing}
The effect of windowing may be  exemplified by use of the Hanning window, which is very popular.  In a nutshell, the Hanning window is effective in reducing  the leakage errors, but  with a trade off of increased interpolation errors. %This is because the term $G_0(\Omega_k)U_0(k)$ in equation \eqref{lpmtd1} is not smooth and $G_0(\Omega_k)$ varies with the frequency. 
Pertinent details of the Hanning window are discussed in \citep{Schoukens2006LPM,Antoni2007FRF,Schoukens2009LPM,Wellstead1981} and \citep{Harris1978}.

@@

\paragraph{Formulation of the Linear LS LPM}
The LPM is formulated as a nonparametric local-linear-least-squares (LS) estimate using the full data record of length $N$ as outlined below \citep{Schoukens2009LPM}. 
\citet[Section 7.2.2]{Pintelon2012} gives the general formulation of the \gls{LPM} for \gls{MIMO} systems. 
The formulation in this paper is a summary for a \gls{SISO} system.

@@

The smooth characteristics of $G_0(\Omega_k)$ and $T(\Omega_k)$ allow for the use of the Taylor series representations at the frequency lines $k+r$ in a frequency domain window of width $2n+1$, with a remainder $\mathcal{O}\left(\frac{r}{N}\right)^{(R+1)}$ of the first order Taylor series expansion \citep{Schoukens2009LPM}, \emph{viz}:
\TODO{ordos are incorrect: notation-wise}
\begin{align}\label{lpmGTaylorS}
G_0(\Omega_{k+r})&=G_0(\Omega_k)+\sum_{p=1}^{R}g_p(k)r^p+\mathcal{O}\left(\frac{r}{N}\right)^{(R+1)},
\\
\label{lpmTTaylorS}
T(\Omega_{k+r})&=T(\Omega_k)+\sum_{p=1}^{R}t_p(k)r^p+N^{-1/2}\mathcal{O}\left(\frac{r}{N}\right)^{(R+1)},
\\
\text{where}&\ r\in\mathbb{W}_n,\quad \mathbb{W}_n = \{-n,-n+1,\dots,n\}
\end{align}

@@

The formulation of equation \eqref{eq:LSsolutionLPM} must take into account the fact that  a full rank of $K_n$ requires $n \geq R + 1$. The choice $n = R + 1$ results in the highest variance on the estimate, but with the smallest interpolation error \citep{Schoukens2009LPM}. %(per JL)!

@@

\TODO{fix reference Section II}
Smoothing of the estimated \gls{FRF} requires the correct estimate of the impulse response. Unfortunately, the \gls{LPM} presented in \secref{se:theoryLPMandWindowing} and in \citep{Schoukens2009LPM} does not estimate the \gls{FRF}  at the frequency $\Omega_0$ (i.e. \gls{DC} value of the \gls{FRF}), hence the subscript $\setminus\mathrm{DC}$ in equation \eqref{eq:impRespiDFT}. Consequently, the mean value of the corresponding estimated impulse response given in equation \eqref{eq:impRespiDFT} is not correct. This anomaly is rectified by developing a simple estimator of the mean value, presented below.

### 2015-12-07 ch05-initvals/InitialValuesPaper.tex
Fix bibliography

The task of interpreting measurement data from dynamic systems often involves the estimation of a transfer function (TF). 
Typical measurement techniques and identification strategies of transfer functions (TFs) or frequency response functions (FRFs) are discussed in \citep{Schoukens1998ImprFRFmeas,Schoukens2006LPM,Guillaume1996,broersen1995transferfunction,Pintelon2010LPM1,Antoni20071723}.
Application of these methods to real devices and systems is well-known in published literature, including \citep{Lim2010,Robinson1990,Behjat2010}.

Parametric identification of linear time-invariant (LTI) systems from input/output data has been well developed as evidenced by published literature~\citep{Pintelon2012,Ljung1999,schoukens1999,pintGuil1998}. 
 Maximizing the likelihood function of the parameters probably yields the most popular, consistent and efficient estimator. 
 However, in a noisy environment, the maximum likelihood estimator (MLE) engenders a nonlinear optimization which, at the very least, requires good initial estimates to avoid local optima.
 Such local optima have a detrimental effect on the quality of the estimated model.

@@

The main aim and contribution of this article is to demonstrate that smoothing a measured FRF helps to avoid local optima during the parametric estimation of the MLE of a transfer function, using deterministic optimization algorithms.
Hence, such techniques make it possible to increase the ``success rate'' (i.e. the probability that a good model, or even the global optimum, is obtained) of such a system identification step considerably.
%Such techniques, hence allow to increase the ``success rate'' (i.e. the probability that a good model, or even the global optimum, is obtained) of such a system identification step considerably.

In particular, two different smoothing techniques --- the time-truncated Local Polynomial Method (LPM)~\citep{Lumori2014} and the regularized finite-impulse response (RFIR)~\citep{Pillonetto201081,Chen20121525} --- are tested for different SNRs and different measurement record lengths of the input/output data of a few single-input-single-output (SISO) LTI systems.
These are compared with the existing initialization schemes, namely: (i) the generalized total least squares (GTLS), and (ii) the bootstrapped total least squares (BTLS).
%The existing initialization schemes compared with are the generalized total least squares (GTLS) and bootstrapped total least squares (BTLS).

The rest of the paper is structured as follows. Section~\ref{se:ProbForm} covers the problem formulation. Section~\ref{se:MethodEg} discusses the methodology for obtaining the initial estimates, and their influence on the success rate of the MLE. 
This is followed by Sections~\ref{se:Demo} and \ref{se:ExpMeas}, which are demonstrations of the improved initial estimates by simulation and experimental data, respectively.
In Section~\ref{se:Generality} the generality of the results is discussed briefly.
Ultimately, concluding remarks are presented in Section~\ref{se:Conclusion}.

@@

The \gls{GTLS} and the \gls{BTLS} have been discussed in \citep{pintGuil1998}. These are modifications of equation \eqref{eq:MLEcf}, which still take into account the noise information while retaining the quadratic nature w.r.t. $\theta$. 
These estimators preserve consistency, such that the estimates converge asymptotically to the true parameters for $N\to\infty$. 
Their finite sample behavior, however, is suitable for improvement by the \gls{FRF} smoothing tools as described below.

@@

A reliably good estimate of the FRF of the chosen system can be obtained via the LPM, which is summarized as follows~\citep{Lumori2014}. Formulated as a nonparametric linear-least-squares-estimate, the LPM is first applied to estimate the FRF from a full data record of a SISO system, systematically expressed in an output-error framework, shown in \figref{fig:oesetup}. The smooth characteristics of both the exact \gls{FRF} $G_0$ and the transient term $T$ allow for an optimal application of the \gls{LPM}, leading to a smooth \gls{FRF} estimate with the transient suppressed.

  With reference to a detailed discussion in~\citep{Lumori2014}, the \gls{LPM} utilizes the following quadratic local polynomials to approximate (in least squares sense) and, thus, smooth $G_0$ and $T$ around a central frequency $\Omega_{k}$ in a local frequency band $r\in\mathbb{W}_n$
\begin{subequations}\label{lpmImplQuadG}
\begin{align}
G_0(\Omega_{k+r})&\approx \hat G_k + g_{1,k} r + g_{2,k}r^2
\\
T(\Omega_{k+r})&\approx T(\Omega_k)+t_{1,k}r + t_{2,k}r^2\label{lpmImplQuadT}
\end{align}
\end{subequations}
where, in general,$\ r\in\mathbb{W}_n,\quad$$\mathbb{W}_n = \{-n,-n+1,\dots,n\}$ and $n$ is a tunable parameter. In this paper, $n=3$.

@@

\emph{Impulse response truncation}. 
%\comment{JL: in this paper, the impulse response truncation as an initial estimator is considered together with the LPM. So I would not start a new subsection for it.}
The estimate is smoothed further by truncating its impulse response function $g_{\text{poly}}(t) = \mathrm{IDFT}\, \left( \hat{G}_\text{poly}(\Omega_k)) \right)$ as originally presented in~\citep{Lumori2014}.
%\comment{JL: $\hat{G}_\text{poly}(\Omega_k))$ is undefined}.

The impulse response is truncated after the time $\tau_{\mathrm{trunc}}$ where the signal becomes indistinguishable from the noise, i.e.
\begin{equation}
  g_{\mathrm{trunc}}(t) = 
  \begin{cases}
    g_{\text{poly}}(t) & t \leq \tau_{\mathrm{trunc}} \\
    0                    & t \geq \tau_{\mathrm{trunc}}
  \end{cases}
  \text{.}
\end{equation}
To this end, an estimate of the envelope of impulse response is determined by fitting an exponential function $g_{\mathrm{exp}}(t) = B e^{\beta t}$ to the peaks of the impulse response $\abs{g_{\mathrm{poly}}(t)}$ using a linear least-squares approach.
Then, $\tau_{\mathrm{trunc}}$ is determined as the time instant where this envelope function sinks below the noise level $\sigma_g$ of the impulse response, i.e. 
\begin{equation}
  \tau_{\mathrm{trunc}} = \min \left\{  t :  g_{\mathrm{exp}}(t) < \gamma \sigma_g \right\}
  = \beta^{-1} \ln \frac{\gamma \sigma_g}{B}
  \text{,}
\end{equation}
where $\gamma=1$ was used in this paper for simplicity.
By changing $\gamma$, the user can fine-tune the bias/variance trade-off of the estimated FRF $G_{\mathrm{trunc}}(\Omega_k) = \mathrm{DFT} \left( g_{\mathrm{trunc}}(t)\right)$ further.
This can lead to a significant improvement over the classical LPM~\citep{Lumori2014}.

@@

An implementation of the \gls{RFIR} estimator is available as the \code{arx} function in the System Identification Toolbox since \MATLAB~2013b with $\mathtt{na} = 0$, $\mathtt{nb} = n_g$, $\mathtt{nk}=0$ and regularization enabled in \code{arxoptions}. 
The hyperparameters can be determined via \code{arxregul}.
More information about the \gls{RFIR} estimator can be found in
~\citep{Pillonetto201081,Chen20121525}. 
The \gls{DFT} of the obtained regularized estimate of the impulse response $\hat g_{\mathrm{RFIR}}$ of the system yields a smoothed estimate of the FRF.
%\JL{Having obtained a regularized estimate of the impulse response of the system, its DFT (Discrete Fourier Transform) yields an estimate of the FRF.}
\end{enumerate}

@@

In \figref{fig:successRateVS_SNR36N3dB}, the success rate (and its $95\%$ confidence interval) obtained from the Monte Carlo simulations is shown to compare the proposed method with previously existing approaches.
The confidence intervals are calculated via the Clopper-Pearson method~\citep{Clopper1934} (as implemented in \MATLAB's \code{binofit}).
This is known to yield somewhat conservative bounds, especially if only failures or successes are observed~\citep{Ross2003}.
Consequently, the improvements observed in \figref{fig:successRateVS_SNR36N3dB} underestimate the actual improvement slightly.

>>>>

The task of interpreting measurement data from dynamic systems often involves the estimation of a transfer function (TF). 
Typical measurement techniques and identification strategies of transfer functions (TFs) or \glspl{FRF} are discussed in \citep{Schoukens1998,Schoukens2006LPM,Guillaume1996,Broersen1995,Pintelon2010LPM1,Antoni2007FRF}.
Application of these methods to real devices and systems is well-known in published literature, including \citep{Lim2010,Robinson1990,Behjat2010}.

Parametric identification of \gls{LTI} systems from input/output data has been well developed as evidenced by published literature~\citep{Pintelon2012,Ljung1999,Schoukens1999,Pintelon1998}. 
 Maximizing the likelihood function of the parameters probably yields the most popular, consistent and efficient estimator. 
 However, in a noisy environment, the \gls{MLE} engenders a nonlinear optimization which, at the very least, requires good initial estimates to avoid local optima.
 Such local optima have a detrimental effect on the quality of the estimated model.

@@

The main aim and contribution of this article is to demonstrate that smoothing a measured \gls{FRF} helps to avoid local optima during the parametric estimation of the \gls{MLE} of a transfer function, using deterministic optimization algorithms.
Hence, such techniques make it possible to increase the ``success rate'' (i.e. the probability that a good model, or even the global optimum, is obtained) of such a system identification step considerably.
%Such techniques, hence allow to increase the ``success rate'' (i.e. the probability that a good model, or even the global optimum, is obtained) of such a system identification step considerably.

In particular, two different smoothing techniques --- the time-truncated \gls{LPM}~\citep{Lumori2014TIM} and the \gls{RFIR}~\citep{Pillonetto2010,Chen2012} --- are tested for different \glspl{SNR} and different measurement record lengths of the input/output data of a few \gls{SISO} \gls{LTI} systems.
These are compared with the existing initialization schemes, namely: (i) the \gls{GTLS}, and (ii) the \gls{BTLS}.
%The existing initialization schemes compared with are the generalized total least squares (GTLS) and bootstrapped total least squares (BTLS).

The rest of the paper is structured as follows. Section~\ref{se:ProbForm} covers the problem formulation. Section~\ref{se:MethodEg} discusses the methodology for obtaining the initial estimates, and their influence on the success rate of the \gls{MLE}. 
This is followed by Sections~\ref{se:Demo} and \ref{se:ExpMeas}, which are demonstrations of the improved initial estimates by simulation and experimental data, respectively.
In Section~\ref{se:Generality} the generality of the results is discussed briefly.
Ultimately, concluding remarks are presented in Section~\ref{se:Conclusion}.

@@

The \gls{GTLS} and the \gls{BTLS} have been discussed in \citep{Pintelon1998}. These are modifications of equation \eqref{eq:MLEcf}, which still take into account the noise information while retaining the quadratic nature w.r.t. $\theta$. 
These estimators preserve consistency, such that the estimates converge asymptotically to the true parameters for $N\to\infty$. 
Their finite sample behavior, however, is suitable for improvement by the \gls{FRF} smoothing tools as described below.

@@

A reliably good estimate of the FRF of the chosen system can be obtained via the LPM, which is summarized as follows~\citep{Lumori2014TIM}. Formulated as a nonparametric linear-least-squares-estimate, the LPM is first applied to estimate the FRF from a full data record of a SISO system, systematically expressed in an output-error framework, shown in \figref{fig:oesetup}. The smooth characteristics of both the exact \gls{FRF} $G_0$ and the transient term $T$ allow for an optimal application of the \gls{LPM}, leading to a smooth \gls{FRF} estimate with the transient suppressed.

  With reference to a detailed discussion in~\citep{Lumori2014TIM}, the \gls{LPM} utilizes the following quadratic local polynomials to approximate (in least squares sense) and, thus, smooth $G_0$ and $T$ around a central frequency $\Omega_{k}$ in a local frequency band $r\in\mathbb{W}_n$
\begin{subequations}\label{lpmImplQuadG}
\begin{align}
G_0(\Omega_{k+r})&\approx \hat G_k + g_{1,k} r + g_{2,k}r^2
\\
T(\Omega_{k+r})&\approx T(\Omega_k)+t_{1,k}r + t_{2,k}r^2\label{lpmImplQuadT}
\end{align}
\end{subequations}
where, in general,$\ r\in\mathbb{W}_n,\quad$$\mathbb{W}_n = \{-n,-n+1,\dots,n\}$ and $n$ is a tunable parameter. In this paper, $n=3$.

@@

\emph{Impulse response truncation}. 
%\comment{JL: in this paper, the impulse response truncation as an initial estimator is considered together with the LPM. So I would not start a new subsection for it.}
The estimate is smoothed further by truncating its impulse response function $g_{\text{poly}}(t) = \mathrm{IDFT}\, \left( \hat{G}_\text{poly}(\Omega_k)) \right)$ as originally presented in~\citep{Lumori2014TIM}.
%\comment{JL: $\hat{G}_\text{poly}(\Omega_k))$ is undefined}.

The impulse response is truncated after the time $\tau_{\mathrm{trunc}}$ where the signal becomes indistinguishable from the noise, i.e.
\begin{equation}
  g_{\mathrm{trunc}}(t) = 
  \begin{cases}
    g_{\text{poly}}(t) & t \leq \tau_{\mathrm{trunc}} \\
    0                    & t \geq \tau_{\mathrm{trunc}}
  \end{cases}
  \text{.}
\end{equation}
To this end, an estimate of the envelope of impulse response is determined by fitting an exponential function $g_{\mathrm{exp}}(t) = B e^{\beta t}$ to the peaks of the impulse response $\abs{g_{\mathrm{poly}}(t)}$ using a linear least-squares approach.
Then, $\tau_{\mathrm{trunc}}$ is determined as the time instant where this envelope function sinks below the noise level $\sigma_g$ of the impulse response, i.e. 
\begin{equation}
  \tau_{\mathrm{trunc}} = \min \left\{  t :  g_{\mathrm{exp}}(t) < \gamma \sigma_g \right\}
  = \beta^{-1} \ln \frac{\gamma \sigma_g}{B}
  \text{,}
\end{equation}
where $\gamma=1$ was used in this paper for simplicity.
By changing $\gamma$, the user can fine-tune the bias/variance trade-off of the estimated FRF $G_{\mathrm{trunc}}(\Omega_k) = \mathrm{DFT} \left( g_{\mathrm{trunc}}(t)\right)$ further.
This can lead to a significant improvement over the classical LPM~\citep{Lumori2014TIM}.

@@

An implementation of the \gls{RFIR} estimator is available as the \code{arx} function in the System Identification Toolbox since \MATLAB~2013b with $\mathtt{na} = 0$, $\mathtt{nb} = n_g$, $\mathtt{nk}=0$ and regularization enabled in \code{arxoptions}. 
The hyperparameters can be determined via \code{arxregul}.
More information about the \gls{RFIR} estimator can be found in
~\citep{Pillonetto2010,Chen2012}. 
The \gls{DFT} of the obtained regularized estimate of the impulse response $\hat g_{\mathrm{RFIR}}$ of the system yields a smoothed estimate of the FRF.
%\JL{Having obtained a regularized estimate of the impulse response of the system, its DFT (Discrete Fourier Transform) yields an estimate of the FRF.}
\end{enumerate}

@@

In \figref{fig:successRateVS_SNR36N3dB}, the success rate (and its $95\%$ confidence interval) obtained from the Monte Carlo simulations is shown to compare the proposed method with previously existing approaches.
The confidence intervals are calculated via the Clopper-Pearson method~\citep{Clopper1934} (as implemented in \MATLAB's \code{binofit}).
\TODO{meer uitleg over Clopper-Pearson}
This is known to yield somewhat conservative bounds, especially if only failures or successes are observed~\citep{Ross2003}.
Consequently, the improvements observed in \figref{fig:successRateVS_SNR36N3dB} underestimate the actual improvement slightly.
